\huge \systemEnding: Growing Libraries of Concepts with Wake-Sleep Program Induction

### 2018-07-23 misc2.tex
Figure ?improvements?

  \node[latent,scale=3] at (3.5,3) (dx){DSL};
  \node[latent,scale=3] at ([yshift=-1.5cm]dx) (zp){prog};
  \node[obs,scale=3] at ([yshift=-2cm]zp) (xp) {data};
  \node[latent,scale=3] at ([xshift=2cm]zp) (zp1){prog};
  \node[obs,scale=3] at ([xshift=2cm]xp) (xp1) {data};
  \draw [->] (zp1.south) -- (xp1.north);
  \draw [->] (dx.south) -- (zp1.north);
  \draw [->,red] (xp1.east) to[out = 30,in = -30] node(nn){} (zp1.east);
%  \node at (nn) {\NeuralNetwork{0.5}};

  \node[latent,scale=3] at ([xshift=-2cm]zp) (zp1){prog};
  \node[obs,scale=3] at ([xshift=-2cm]xp) (xp1) {data};
  \draw [->] (zp1.south) -- (xp1.north);
  \draw [->] (dx.south) -- (zp1.north);
  \draw [->,red] (xp1.east) to[out = 30,in = -30] node(nn){} (zp1.east);
%  \node at (nn) {\NeuralNetwork{0.5}};

  \draw [->,red] (xp.east) to[out = 30,in = -30] node(nn){} (zp.east);
  \node at (nn) {\NeuralNetwork{0.5}};
  \draw [->] (dx.south) -- (zp.north);
  \draw [->] (zp.south) -- (xp.north);

  %\node[shift={+(0,-1.7)}] at (nn) { $Q$  };

@@

    \draw [->,dashed] (DSL.north) to[out = 90,in = 180] node[fill=white,align = center]{  \footnotesize{Inductive bias}\\\footnotesize{(Wake)}} (synthesis.west);
    \draw [->,dashed] (recognitionModel.north) to[out = 90,in = 0] node[fill=white,align = center]{{\footnotesize Makes tractable}\\{\footnotesize (Wake)}} (synthesis.east);
  \end{scope}
    \end{tikzpicture}
 % \caption{\system solves for programs, the DSL, and a recognition model. Each of these steps bootstrap off of the others in a Helmholtz-machine inspired wake/sleep inference algorithm.}  \label{feeding}
\end{figure}
%% \begin{itemize}
%% \item Search finds new programs$\implies$ DSL+recognition model get more data
%% \item DSL improves$\implies$easier search, recognition model gets better data
%%   \item Recognition model improves$\implies$ easier search
%%   \end{itemize}

>>>>

  \node[latent,scale=3] at (3.5,3) (dx){DSL};
  \node[latent,scale=3] at ([yshift=-1.5cm,xshift=2cm]dx) (zp){prog};
  \node[obs,scale=3] at ([yshift=-2cm]zp) (xp) {data};
  \node[latent,scale=3] at ([xshift=2cm]zp) (zp1){prog};
  \node[obs,scale=3] at ([xshift=2cm]xp) (xp1) {data};
  \draw [->] (zp1.south) -- (xp1.north);
  \draw [->] (dx.south) -- (zp1.north);
  \draw [->,red] (xp1.east) to[out = 30,in = -30] node(nn){} (zp1.east);

  \node[latent,scale=3] at ([xshift=-2cm]zp) (zp1){prog};
  \node[obs,scale=3] at ([xshift=-2cm]xp) (xp1) {data};
  \draw [->] (zp1.south) -- (xp1.north);
  \draw [->] (dx.south) -- (zp1.north);
  \draw [->,red] (xp1.east) to[out = 30,in = -30] node(nn){} (zp1.east);

  \draw [->,red] (xp.east) to[out = 30,in = -30] node(nn){} (zp.east);
  \draw [->] (dx.south) -- (zp.north);
  \draw [->] (zp.south) -- (xp.north);

  \draw [->,red] ([xshift=2cm]dx.east) -- ([xshift=3cm]dx.east);
  \node at ([xshift=3.2cm]dx.east]) (uses){is};k
  \node at ([xshift=0.5cm]uses.east) (nnn){\NeuralNetwork{0.5}};
  \draw[thin] ([xshift=1.9cm,yshift=0.4cm]dx.east) rectangle
  ([xshift=0.5cm,yshift=-0.3cm]nnn.south);

@@

    \draw [->,dashed] (DSL.north) to[out = 90,in = 180] node[fill=white,align = center]{  \footnotesize{Inductive bias}\\\footnotesize{(Wake)}} (synthesis.west);
    \draw [->,dashed] (recognitionModel.north) to[out = 90,in = 0] node[fill=white,align = center]{{\footnotesize Makes tractable}\\{\footnotesize (Wake)}} (synthesis.east);
  \end{scope}
    \end{tikzpicture}
  \caption{~\system solves for programs, the DSL, and a recognition model. Each of these steps bootstrap off of the others in a Helmholtz-machine inspired wake/sleep inference algorithm.}  \label{feeding}
\end{figure}
%% \begin{itemize}
%% \item Search finds new programs$\implies$ DSL+recognition model get more data
%% \item DSL improves$\implies$easier search, recognition model gets better data
%%   \item Recognition model improves$\implies$ easier search
%%   \end{itemize}
